Untitled

### 2023-08-14 code/analysis_Redo.Rmd
updated with dist delta b

did2s(
      data = df.sum , 
      yname = "Altmans.Z", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
  filter(Year %in% c(2015, 2019)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
  mutate(ds = `2019` - `2015`) %>% 
    ungroup() %>% 
    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 0),#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
    filter(Year == 2016) %>% select(`Grant Number`, avgdist), by = c("Grant Number")) ,#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
        cluster_var = "ID",
      verbose = FALSE
    )

>>>>

did2s(
      data = df.sum %>% inner_join(df.qual.exp %>% filter(MarketShare > 1) %>% select(`Grant Number`) %>% unique(), by = c("Grant Number")), 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
  filter(Year %in% c(2015, 2019)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
  mutate(ds = `2019` - `2015`) %>% 
    ungroup() %>% 
    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(ds < 1),#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) , by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% inner_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite < 5),
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) ,
        cluster_var = "ID",
      verbose = FALSE
    )
